
Countries of occurrence were extracted by overlapping the distribution saved in step 1 with a map of countries matching the list of countries and subnational entities from the Red List (see the sRedList documentation for further details). As you selected the species occurs in the system(s): `r outlog$Value[outlog$Parameter=="System_pref"]`, we used a `r c(ifelse(grepl("Terrestrial", outlog$Value[outlog$Parameter=="System_pref"]) | grepl("Freshwater", outlog$Value[outlog$Parameter=="System_pref"]), "terrestrial", NA), ifelse(grepl("Marine", outlog$Value[outlog$Parameter=="System_pref"]), "marine (using EEZs)", NA)) %>% .[is.na(.)==F] %>% paste(., collapse=" and ")` map of countries. The following map was obtained:

```{r leaflet_coo, fig.align = "center", out.width = '100%'}
Storage_SP$Leaflet_COO
```

The list of realms is: `r paste0(unlist(strsplit(Storage_SP$Realms_saved, "[|]")), collapse=", ")`

`r if("FAO_sp" %in% names(Storage_SP)){if(nrow(Storage_SP$FAO_sp)>0){"The list of FAO major fishing regions is: "}}`

```{r print_fao, out.width='100%'}
if("FAO_sp" %in% names(Storage_SP)){if(nrow(Storage_SP$FAO_sp)>0){
  FAO_to_print <- Storage_SP$FAO_sp[, c("FAO_CODE", "Name", "presence", "origin", "seasonal")]
  FAO_to_print <- FAO_to_print[order(FAO_to_print$FAO_CODE),]
  FAO_to_print$geometry <- FAO_to_print$geom <- NULL
  
  DT::datatable(FAO_to_print, 
                 rownames=F,
                 options=list(
                   pageLength = 20
                 )
  )
  
}}
```


The list of countries of occurrence is`r if("COO_EditShiny" %in% outlog$Parameter){" (after it was manually edited through the interactive map)"}`:

```{r print_coo, out.width='100%'}
COO_df<-Storage_SP$coo_occ %>% as.data.frame(.) %>% .[, ! names(.) %in% c("geometry", "Popup", "colour", "Domain", "Level0_occupied", "Level1_occupied", "lookup_SIS0")]

DT::datatable(COO_df, rownames=F,
              options=list(
                pageLength = 20,
                headerCallback = DT::JS(# Needed to reduce column name font
                  "function(thead) {",
                  "  $(thead).css('font-size', '0.75em');",
                  "}"))
) %>% DT::formatStyle(columns = c(1:ncol(COO_df)), fontSize = '75%')
```

*Note that if multiple presence or origin codes are selected for a single entity, the platform will only keep the appropriate value (following the hierarchy described in the Mapping Standards) in the outputs (countries.csv).*

