

Trends in some remote-sensing products have been calculated. You can check the sRedList documentation to know more on the products we map.

<br>


`r if(grepl("Forest_cover", outlog$Value[outlog$Parameter=="Usage_RS"])){"You mapped and calculated trends in Forest Cover using Global Forest Change rasters."}`
<center>
![](`r if(grepl("Forest_cover", outlog$Value[outlog$Parameter=="Usage_RS"])){paste0(outDir, '/Plots/RS_plot_forest.png')}`){width=100%}
</center>

```{r trends_forest, out.width='100%'}
if(grepl("Forest_cover", outlog$Value[outlog$Parameter=="Usage_RS"])){
  DF_forest<-data.frame(Calc=c("Current value", "Absolute trends", "Relative trends", "Time-window"), Value=unlist(strsplit(outlog$Value[outlog$Parameter=="RS_result_Forest_cover"], " & ")))
  knitr::kable(DF_forest, "simple", col.names = c("", "Value"))
}
```

```{r leaflet_forest, fig.align = "center", out.width = '100%'}
if("RS_leaflet_Forest_cover" %in% names(Storage_SP)){Storage_SP$RS_leaflet_Forest_cover}
```




`r if(grepl("Forest_Integrity", outlog$Value[outlog$Parameter=="Usage_RS"])){"You mapped and calculated Forest Integrity using rasters from Grantham et al 2020."}`
<center>
![](`r if(grepl("Forest_Integrity", outlog$Value[outlog$Parameter=="Usage_RS"])){paste0(outDir, '/Plots/RS_plot_forestintegrity.png')}`){width=100%}
</center>

```{r forest_integrity, out.width='100%'}
if(grepl("Forest_Integrity", outlog$Value[outlog$Parameter=="Usage_RS"])){
  DF_integrity<-data.frame(Calc=c("Current value", "Percentages", "Time-window"), Value=unlist(strsplit(outlog$Value[outlog$Parameter=="RS_result_Forest_Integrity"], " & "))[1:3])
  knitr::kable(DF_integrity, "simple", col.names = c("", "Value"))
}
```

```{r leaflet_integrity, fig.align = "center", out.width = '100%'}
if("RS_leaflet_Forest_Integrity" %in% names(Storage_SP)){Storage_SP$RS_leaflet_Forest_Integrity}
```




`r if(grepl("Human_modification", outlog$Value[outlog$Parameter=="Usage_RS"])){"<br>You mapped and calculated trends in human modification using Theobald et al. (2020) data."}`
<center>
![](`r if(grepl("Human_modification", outlog$Value[outlog$Parameter=="Usage_RS"])){paste0(outDir, '/Plots/RS_plot_modif.png')}`){width=100%}
</center>

```{r trends_modification, out.width='100%'}
if(grepl("Human_modification", outlog$Value[outlog$Parameter=="Usage_RS"])){
  DF_modif<-data.frame(Calc=c("Current value", "Absolute trends", "Relative trends", "Time-window"), Value=unlist(strsplit(outlog$Value[outlog$Parameter=="RS_result_Human_modification"], " & ")))
  knitr::kable(DF_modif, "simple", col.names = c("", "Value"))
}
```

```{r leaflet_modif, fig.align = "center", out.width = '100%'}
if("RS_leaflet_Human_modification" %in% names(Storage_SP)){Storage_SP$RS_leaflet_Human_modification}
```




`r if(grepl("Human_density", outlog$Value[outlog$Parameter=="Usage_RS"])){"<br>You mapped and calculated trends in human population density using the Global Human Settlement dataset."}`
<center>
![](`r if(grepl("Human_density", outlog$Value[outlog$Parameter=="Usage_RS"])){paste0(outDir, '/Plots/RS_plot_humandensity.png')}`){width=100%}
</center>

```{r trends_density, out.width='100%'}
if(grepl("Human_density", outlog$Value[outlog$Parameter=="Usage_RS"])){
  DF_density<-data.frame(Calc=c("Current value", "Absolute trends", "Relative trends", "Time-window"), Value=unlist(strsplit(outlog$Value[outlog$Parameter=="RS_result_Human_density"], " & ")))
  knitr::kable(DF_density, "simple", col.names = c("", "Value"))
}
```

```{r leaflet_density, fig.align = "center", out.width = '100%'}
if("RS_leaflet_Human_density" %in% names(Storage_SP)){Storage_SP$RS_leaflet_Human_density}
```



`r if(grepl("Water_availability", outlog$Value[outlog$Parameter=="Usage_RS"])){"<br>You mapped and calculated trends in inland water availability using the Global Surface Water dataset."}`
<center>
![](`r if(grepl("Water_availability", outlog$Value[outlog$Parameter=="Usage_RS"])){paste0(outDir, '/Plots/RS_plot_water.png')}`){width=100%}
</center>

```{r trends_water, out.width='100%'}
if(grepl("Water_availability", outlog$Value[outlog$Parameter=="Usage_RS"])){
  DF_water<-data.frame(Calc=c("Current value", "Absolute trends", "Relative trends", "Time-window"), Value=unlist(strsplit(outlog$Value[outlog$Parameter=="RS_result_Water_availability"], " & ")))
  knitr::kable(DF_water, "simple", col.names = c("", "Value"))
}
```

```{r leaflet_water, fig.align = "center", out.width = '100%'}
if("RS_leaflet_Water_availability" %in% names(Storage_SP)){Storage_SP$RS_leaflet_Water_availability}
```





`r if(grepl("Marine_impact", outlog$Value[outlog$Parameter=="Usage_RS"])){"<br>You mapped and calculated trends in human impact on marine ecosystems using data from Halpern et al 2015."}`
<center>
![](`r if(grepl("Marine_impact", outlog$Value[outlog$Parameter=="Usage_RS"])){paste0(outDir, '/Plots/RS_plot_marineimpact.png')}`){width=100%}
</center>

```{r trends_MarineImpact, out.width='100%'}
if(grepl("Marine_impact", outlog$Value[outlog$Parameter=="Usage_RS"])){
  DF_marine<-data.frame(Calc=c("Current value", "Absolute trends", "Time-window"), Value=unlist(strsplit(outlog$Value[outlog$Parameter=="RS_result_Marine_impact"], " & "))[1:3])
  knitr::kable(DF_marine, "simple", col.names = c("", "Value"))
}
```

```{r leaflet_MarineImpact, fig.align = "center", out.width = '100%'}
if("RS_leaflet_Marine_impact" %in% names(Storage_SP)){Storage_SP$RS_leaflet_Marine_impact}
```

