
Countries of occurrence were extracted by overlapping the distribution saved in step 1 with a map of countries matching the list of countries and subnational entities from the Red List (see the sRedList documentation for further details). As you selected the species occurs in the system(s): `r outlog$Value[outlog$Parameter=="System_pref"]`, we used a `r c(ifelse(grepl("Terrestrial", outlog$Value[outlog$Parameter=="System_pref"]) | grepl("Freshwater", outlog$Value[outlog$Parameter=="System_pref"]), "terrestrial", NA), ifelse(grepl("Marine", outlog$Value[outlog$Parameter=="System_pref"]), "marine (using EEZs)", NA)) %>% .[is.na(.)==F] %>% paste(., collapse=" and ")` map of countries. The following map was obtained:

```{r leaflet_coo, fig.align = "center", out.width = '100%'}
Storage_SP$Leaflet_COO
```

The list of realms is: `r paste0(unlist(strsplit(Storage_SP$Realms_saved, "[|]")), collapse=", ")`

The list of countries of occurrence is`r if("COO_EditShiny" %in% outlog$Parameter){" (after it was manually edited through the interactive map)"}`:

```{r print_coo, out.width='100%'}
COO_df<-Storage_SP$coo_occ %>% as.data.frame(.) %>% .[, ! names(.) %in% c("geometry", "Popup", "colour", "Domain", "Level0_occupied", "Level1_occupied", "lookup_SIS0")]

DT::datatable(COO_df, rownames=F,
              options=list(
                pageLength = 20,
                headerCallback = DT::JS(# Needed to reduce column name font
                  "function(thead) {",
                  "  $(thead).css('font-size', '0.75em');",
                  "}"))
) %>% DT::formatStyle(columns = c(1:ncol(COO_df)), fontSize = '75%')
```



