
Countries of occurrence were extracted by overlapping the distribution saved in step 1 with a map of countries matching the list of countries and subnational entities from the Red List (see the sRedList documentation for further details). As you selected the species occurs in the system(s): `r outlog$Value[outlog$Parameter=="System_pref"]`, we used a `r c(ifelse(grepl("Terrestrial", outlog$Value[outlog$Parameter=="System_pref"]) | grepl("Freshwater", outlog$Value[outlog$Parameter=="System_pref"]), "terrestrial", NA), ifelse(grepl("Marine", outlog$Value[outlog$Parameter=="System_pref"]), "marine (using EEZs)", NA)) %>% .[is.na(.)==F] %>% paste(., collapse=" and ")` map of countries. `r ifelse(is.na(outlog$Value[outlog$Parameter=="Crop_Country"]), "", paste0("You only kept the part of the distribution that is included in ", outlog$Value[outlog$Parameter=="Crop_Country"], " (National Red Listing option)."))` The following map was obtained:

```{r leaflet_coo, fig.align = "center", out.width = '100%'}
Storage_SP$Leaflet_COO
```

The list of realms is: `r paste0(unlist(strsplit(Storage_SP$Realms_saved, "[|]")), collapse=", ")`

The list of countries of occurrence is:

```{r print_coo, out.width='100%'}
# COO_df<-Storage_SP$coo_occ
# names(COO_df)<-c("Country", "Subnational")
# COO_df$Subnational<-replace(COO_df$Subnational, is.na(COO_df$Subnational), "")
# for(i in which(grepl("<i>", COO_df$Country))){Name<-COO_df$Country[i] %>% sub("<i>", "", .) %>% sub("</i>", "", .) ; if(Name %in% COO_df$Country){COO_df$Country[i]<-Name}} # For each country in italics, I check if it also exists not italics and, if so, write it in regular plain text
# knitr::kable(COO_df, "simple")
HTML(Storage_SP$coo_res)
```

<br>
`r ifelse(grepl("<i>", paste(Storage_SP$coo_res, collapse="")), "Entities are written in italics if they overlap with the polygon distribution but not with occurrence records (they are included in countries.csv in the ZIP output). By default, we assumed for all countries the codes 'Native' for origin, 'Resident' for seasonality. For presence, we assumemd 'Extant' for all countries with occurrence records and 'Possibly Extant' for countries overlapping with the distribution but without occurrence records (i.e., those written in italics)", "By default, we assumed for all countries the codes 'Extant' for presence, 'Native' for origin, 'Resident' for seasonality")`. If you want to edit those, or the list of countries, you will have to do that manually in SIS. If you do not want to use this list at all, you can delete the 'countries.csv' file from the ZIP output.


