

Trends in some remote-sensing products have been calculated. You can check the sRedList documentation to know more on the products we map.

<br>


`r if(grepl("Forest_cover", outlog$Value[outlog$Parameter=="Usage_RS"])){"You mapped and calculated trends in Forest Cover using Global Forest Change rasters."}`

```{r trends_forest, out.width='100%'}
if(grepl("Forest_cover", outlog$Value[outlog$Parameter=="Usage_RS"])){
  png::readPNG(paste0(outDir, "/Plots/RS_plot_forest.png")) %>% grid::rasterGrob() %>% gridExtra::grid.arrange()
  DF_forest<-data.frame(Calc=c("Current value", "Absolute trends", "Relative trends", "Time-window"), Value=unlist(strsplit(outlog$Value[outlog$Parameter=="RS_result_Forest_cover"], " & ")))
  knitr::kable(DF_forest, "simple", col.names = c("", "Value"))
}
```

```{r leaflet_forest, fig.align = "center", out.width = '100%'}
if("RS_leaflet_Forest_cover" %in% names(Storage_SP)){Storage_SP$RS_leaflet_Forest_cover}
```


<br>

`r if(grepl("Human_modification", outlog$Value[outlog$Parameter=="Usage_RS"])){"You mapped and calculated trends in human modification using Theobald et al. (2020) data."}`

```{r trends_modification, out.width='100%'}
if(grepl("Human_modification", outlog$Value[outlog$Parameter=="Usage_RS"])){
  png::readPNG(paste0(outDir, "/Plots/RS_plot_modif.png")) %>% grid::rasterGrob() %>% gridExtra::grid.arrange()
  DF_modif<-data.frame(Calc=c("Current value", "Absolute trends", "Relative trends", "Time-window"), Value=unlist(strsplit(outlog$Value[outlog$Parameter=="RS_result_Human_modification"], " & ")))
  knitr::kable(DF_modif, "simple", col.names = c("", "Value"))
}
```

```{r leaflet_modif, fig.align = "center", out.width = '100%'}
if("RS_leaflet_Human_modification" %in% names(Storage_SP)){Storage_SP$RS_leaflet_Human_modification}
```


<br>

`r if(grepl("Human_density", outlog$Value[outlog$Parameter=="Usage_RS"])){"You mapped and calculated trends in human population density using the Global Human Settlement dataset."}`

```{r trends_density, out.width='100%'}
if(grepl("Human_density", outlog$Value[outlog$Parameter=="Usage_RS"])){
  png::readPNG(paste0(outDir, "/Plots/RS_plot_humandensity.png")) %>% grid::rasterGrob() %>% gridExtra::grid.arrange()
  DF_density<-data.frame(Calc=c("Current value", "Absolute trends", "Relative trends", "Time-window"), Value=unlist(strsplit(outlog$Value[outlog$Parameter=="RS_result_Human_density"], " & ")))
  knitr::kable(DF_density, "simple", col.names = c("", "Value"))
}
```

```{r leaflet_density, fig.align = "center", out.width = '100%'}
if("RS_leaflet_Human_density" %in% names(Storage_SP)){Storage_SP$RS_leaflet_Human_density}
```


