

Trends in some remote-sensing products have been calculated. You can check the sRedList documentation to know more on the products we map.

<br>


`r if(grepl("Forest_cover", outlog$Value[outlog$Parameter=="Usage_RS"])){"You mapped and calculated trends in Forest Cover using Global Forest Change rasters."}`

```{r trends_forest, out.width='100%'}
if(grepl("Forest_cover", outlog$Value[outlog$Parameter=="Usage_RS"])){
  readPNG(paste0("resources/AOH_stored/", sub(" ", "_", scientific_name), "/Plots/RS_plot_forest.png")) %>% rasterGrob() %>% grid.arrange()
  DF_forest<-data.frame(Calc=c("Current value", "Absolute trends", "Relative trends", "Time-window"), Value=unlist(strsplit(outlog$Value[outlog$Parameter=="RS_result_Forest_cover"], " & ")))
  flextable::flextable(DF_forest) %>% flextable::set_table_properties(layout="autofit")
}
```



<br>

`r if(grepl("Human_modification", outlog$Value[outlog$Parameter=="Usage_RS"])){"You mapped and calculated trends in human modification using Theobald et al. (2020) data."}`

```{r trends_modification, out.width='100%'}
if(grepl("Human_modification", outlog$Value[outlog$Parameter=="Usage_RS"])){
  readPNG(paste0("resources/AOH_stored/", sub(" ", "_", scientific_name), "/Plots/RS_plot_modif.png")) %>% rasterGrob() %>% grid.arrange()
  DF_modif<-data.frame(Calc=c("Current value", "Absolute trends", "Relative trends", "Time-window"), Value=unlist(strsplit(outlog$Value[outlog$Parameter=="RS_result_Human_modification"], " & ")))
  flextable::flextable(DF_modif) %>% flextable::set_table_properties(layout="autofit")
}
```



<br>

`r if(grepl("Human_density", outlog$Value[outlog$Parameter=="Usage_RS"])){"You mapped and calculated trends in human population density using the Global Human Settlement dataset."}`

```{r trends_density, out.width='100%'}
if(grepl("Human_density", outlog$Value[outlog$Parameter=="Usage_RS"])){
  readPNG(paste0("resources/AOH_stored/", sub(" ", "_", scientific_name), "/Plots/RS_plot_humandensity.png")) %>% rasterGrob() %>% grid.arrange()
  DF_density<-data.frame(Calc=c("Current value", "Absolute trends", "Relative trends", "Time-window"), Value=unlist(strsplit(outlog$Value[outlog$Parameter=="RS_result_Human_density"], " & ")))
  flextable::flextable(DF_density) %>% flextable::set_table_properties(layout="autofit")
}
```




